### 2018-10-01 Sections/essay_NISQ_QC.tex
essays and references

We have good reasons to believe that a quantum computer can efficiently simulate any process that occurs in nature, we could probe deeply into the properties of complex molecules and materials. This confidence is based quantum complexity arguments, and the eventual capabilities of quantum error correction. Both of these are based on entanglement, a correlation property amongst systems which are uniquely quantum mechanical. We have strong evidence that quantum computers have abilities which surpass classical ones, three are as follows
\begin{itemize}
\item Quantum complexity - the best example is the Shor algorithm \cite{} which can find the factors of large numbers exponentially faster. Whilst we do not have a proof that a classical algorithm does not exist which can efficiently factorise, brilliant mathematicians have been trying for decades without success. Number factorisation has significant impacts on cryptography because its computational complexity underpins all of the modern encryption. 
% 
\item Complexity theory arguments - computer scientists have shown that quantum states which can be easily prepared with a quantum computer have super-classical properties. It is hard for a classical computer to generate the probability distributions for Boson-sampling, but a quantum computer can simply do the experiment.
% 
\item No known classical algorithm can simulate a quantum computer.
\end{itemize}

@@

 The number 50 is a significant milestone because that is what we can simulate by brute force with the most powerful existing computer \cite{}. The main question is when will quantum computes be able to solve useful problems faster than the classical computer?
Here we discuss a few potential uses of NISQ.

\subsection{Quantum optimizers}
For many problems, there is a big gap between the approximation achieved by classical algorithms and the barrier of NP-hardness. Quantum computers are not expected to solve the worst-case NP-hard problems, however, quantum devices may be able to find better approximate solutions to such problems, or find such approximations faster. The vision for using NISQ to solve optimization problems is a hybrid quantum-classical algorithm. In this scheme we use the quantum device to produce a $n-$qubit state, measure the qubits, then process the measurement outcomes classically; then this is used as a feedback in the next quantum state preparation. The cycle is repeated until it converges to a quantum state from which the approximation can be extracted. Two such algorithms go by the name quantum approximate optimization algorithm\cite{}, and variational quantum eigensolver \cite{}.

\subsection{
Quantum machine learning}
Much of the literature build on quantum algorithms which speed up linear algebra
One of the potentials of quantum machine learning rests upon QRAM -- quantum random access memory. For classical data processing, by using QRAM we may be able to represent a large amount of classical data, N-bits, using $\log$N qubits. However, the bottleneck may be in the encoding/decoding of the QRAM, which may eliminate potential advantages. 
It is perhaps more natural to think about quantum machine learning in a setting where both the input an output are quantum states, e.g. to control a quantum system, or in learning probability distributions where entanglement plays an important role.

@@

A quantum algorithm has shown to find an approximate solution to the problem with an exponential speed up \cite{}. In the algorithm, the initial state is a thermal Gibbs state associated with a Hamiltonian that is the linear combination of the input matrices for the semidefinite program. The success of the implementation depends on whether the particular thermal state can be efficiently prepared. 
The output is a quantum state $\rho$ which approximates the optimal matrix. The quantum state can be measured to extract information on the matrix.

>>>>

We have good reasons to believe that a quantum computer can efficiently simulate any process that occurs in nature, we could probe deeply into the properties of complex molecules and materials. This confidence is based quantum complexity arguments, and the eventual capabilities of quantum error correction. Both of these are based on entanglement, a correlation property amongst systems which are uniquely quantum mechanical. We have strong evidence that quantum computers have abilities which surpass classical ones, three are as follows
\begin{itemize}
\item Quantum complexity - the best example is the Shor algorithm \cite{shor1994algorithms} which can find the factors of large numbers exponentially faster. Whilst we do not have a proof that a classical algorithm does not exist which can efficiently factorise, brilliant mathematicians have been trying for decades without success. Number factorisation has significant impacts on cryptography because its computational complexity underpins all of the modern encryption. 
% 
\item Complexity theory arguments - computer scientists have shown that quantum states which can be easily prepared with a quantum computer have super-classical properties. It is hard for a classical computer to generate the probability distributions for Boson-sampling, but a quantum computer can simply do the experiment.
% 
\item No known classical algorithm can simulate a quantum computer.
\end{itemize}

@@

 The number 50 is a significant because that is the number of qubits we can still simulate by brute force with the most powerful existing computer \cite{}. The main question is: when will quantum computes be able to solve useful problems faster than the classical computer?
Here we discuss a few potential uses of NISQ.

\subsection{Quantum optimizers}
For many problems, there is a big gap between the approximation achieved by classical algorithms and the barrier of NP-hardness. Quantum computers are not expected to solve the worst-case NP-hard problems, however, quantum devices may be able to find better approximate solutions to such problems, or find such approximations faster. The vision for using NISQ to solve optimization problems is a hybrid quantum-classical algorithm. In this scheme we use the quantum device to produce a $n-$qubit state, measure the qubits, then process the measurement outcomes classically; then this is used as a feedback in the next quantum state preparation. The cycle is repeated until it converges to a quantum state from which the approximation can be extracted. Two such algorithms go by the name quantum approximate optimization algorithm\cite{farhi2014quantum}, and variational quantum eigensolver \cite{mcclean2016theory}.

\subsection{Quantum machine learning}
Much of the literature build on quantum algorithms which speed up linear algebra\cite{biamonte2017quantum}.
One of the potentials of quantum machine learning rests upon QRAM -- quantum random access memory. For classical data processing, by using QRAM we may be able to represent a large amount of classical data, N-bits, using $\log$N qubits. However, the bottleneck may be in the encoding/decoding of the QRAM, which may eliminate potential advantages. 
It is perhaps more natural to think about quantum machine learning in a setting where both the input an output are quantum states, e.g. to control a quantum system, or in learning probability distributions where entanglement plays an important role.

@@

A quantum algorithm has shown to find an approximate solution to the problem with an exponential speed up \cite{brandao2017quantum,brandao2017exponential}. In the algorithm, the initial state is a thermal Gibbs state associated with a Hamiltonian that is the linear combination of the input matrices for the semidefinite program. The success of the implementation depends on whether the particular thermal state can be efficiently prepared. 
The output is a quantum state $\rho$ which approximates the optimal matrix. The quantum state can be measured to extract information on the matrix.
